# Assignment 1
========================================================

Loading data:

```{r}
activity <- read.csv("D:/Projects/GitHub/ReproducibleResearch/activity.csv")
```

## Mean total number of steps taken per day

```{r}
activityCleaned <- activity[complete.cases(activity),]
stepsByDay <- tapply(X = activity$steps, INDEX = activity$date, FUN = sum)
totalNumberOfStepsPerDay <- stepsByDay[complete.cases(stepsByDay)]
```

Total number of steps taken per day:
`r totalNumberOfStepsPerDay`

```{r}
hist(totalNumberOfStepsPerDay,main = "Total Number of Steps per Day", xlab = "steps/day")
```

        | value
--------|--------------------------------------
Mean    |`r mean(totalNumberOfStepsPerDay)`
Median  |`r median(totalNumberOfStepsPerDay)`

```{r}
stepsByTimeOfDay <- tapply(X = activityCleaned$steps, INDEX = activityCleaned$interval, FUN = sum)
plot(names(stepsByTimeOfDay), y = stepsByTimeOfDay)
```

Time of highest activity: `r names(stepsByTimeOfDay[which.max(stepsByTimeOfDay)])`

Rows containing NA values: `r nrow(activity)-nrow(activityCleaned)`

```{r}

```
